\section{Problem 6}
\subsection{Problem}
Decide whether there exist infinitely many triples $(a,b,c)$ of positive integers such that all prime factors of $a!+b!+c!$ are smaller than $2020$.
\nl
\textit{Proposed by Pitchayut Saengrungkongka, Thailand}
\subsection{Solutions}
The answer is negative; there are finitely many such triples.
\nl Let $p$ be a prime greater than $2020$ (for example, $p=2027$). Without loss of generality, let $a\leq b\leq c$. If $a\geq p$, then $p\mid a!+b!+c!$ so we are done. Hence let us assume that $a<p$.
\begin{claim}
    $b<a+p<2p$
\end{claim}
\begin{proof}
    Assume that $b\geq a+p$. Then note that $p!a!\mid b!$
    $$\frac{a!+b!+c!}{a!}=1+\frac{b!\cdot k}{a!} = 1+p!\cdot\text{integer}$$
    thus any prime factor of $\tfrac{a!+b!+c!}{a!}$ is greater than $p$. Obviously there exists at least one hence a contradiction.
\end{proof}
\begin{claim}
    $c<p!+(2p)!+p$
\end{claim}
\begin{proof}
    Let $N = p!+(2p)!$. Assume that $c\geq N+p$. Notice that $a!+b!\mid N!$ thus $p!(a!+b!)\mid c!$ which means
    $$\frac{a!+b!+c!}{a!+b!} = 1+p!\cdot\text{integer}$$
    thus any prime factor of $\frac{a!+b!+c!}{a!+b!}$ is greater than $p$. Obviously at least one exists so contradiction.
\end{proof}
The two claims above give the bound for $a,b,c$. Hence there are finitely many tuples.
\begin{remark}
    The problem generalizes to $a_1!+a_2!+\hdots+a_n!$. The proof is basically just keep applying the same argument until you get the bounds of all $a_i$'s, which is quite techical and not worth asking.
\end{remark}
\subsection{Marking Scheme}
To our knowledge, we don't know any substantially different approach to this problem. If such approach happens, it should be judged as equivalently as possible.
\nl The marking scheme is divided into three additive parts. However, the partial credits within each part are \textbf{not additive}.
\nl In what follows, assume that $a\leq b\leq c$.
\begin{enumerate}
        \marking{0}{Examples of non-rewarding observations: any subset of the following.}
        \begin{enumerate}
            \item Try to construct such triples.
            \item Assume that $a\leq b\leq c$ (or similar variants).
            \item Reduce the problem to showing that $c$ is bounded by a constant.
            \item List all primes smaller than 2020.
            \item Correctly guess the answer.
            \item Prove that for a \textbf{chosen} constant $k\in\mathbb{Z}$, there exists only finitely many positive integer $a$ such that all prime factors of $a!+k$ are smaller than $2020$.
            \item Prove the smaller case (i.e. when $2020$ is replaced to smaller number), that does not show the idea of how to do the general case.
        \end{enumerate}
        \marking{1}{Showing that $a$ must be bounded by a constant}
        \marking{3}{Showing that $b$ must be bounded by a constant}
        \begin{enumerate}
                \marking{1}{Make a serious attempt of using the fact that each prime factor of an integer $n\equiv 1\pmod{k!}$ must be greater than $k$, or its similar variants.}
        \end{enumerate}
        \marking{3}{Showing that $c$ must be bounded by a constant}
\end{enumerate}
In addition, points could be given for contestants who have proposed and solved the easier version to this problem. These points are \textbf{not additive} to each other and are \textbf{not additive} to the mainstream progress above.
\begin{enumerate}
        \marking{1}{Prove that for \textbf{any} constant $k\in\mathbb{Z}$, there exists only finitely many positive integer $a$ such that all prime factors of $a!+k$ are smaller than $2020$.}
        \marking{2}{Prove that for there exists only finitely many pairs $(a,b)$ of positive integers such that all prime factors of $a!+b!$ are smaller than $2020$.}
        \marking{5}{Prove that for a \textbf{chosen nonzero} constant $k$, there exists only finitely many pairs $(a,b)$ of positive integers such that all prime factors of $a!+b!+k$ are smaller than $2020$.}
\end{enumerate}
The correct solution should be judged as 7 points. However, the following deductions could be applied.
\begin{enumerate}
        \marking{-0}{The contestant has an incorrect bound which is caused by \textbf{only} miscomputation.}
        \marking{-1}{The contestant has incorrectly do the first part, by claiming the contradiction if $a\geq 2020$, where, in principle $a$ could lie between $2021$ to $2026$ (inclusive).}
        \marking{-1}{The contestant has any other nontrivial minor error.}
\end{enumerate}
