\documentclass{qmo}

\qmotime{Time: 5 hours}
\date{May 17th, 2020}
\level{Advanced level}
\qmoday{Day 2}

\begin{document}
\maketitle
\begin{flushright}
\emph{Each problem is worth 7 points.}\nl
\emph{These problems are to be kept confidential till Monday, 18$^\mathit{th}$ May 2020, 1200 hours (GMT).}
\end{flushright}
\setcounter{problem}{4}
\begin{problem}
	Let $\mathbb{Q}$ denote the set of rational numbers. Determine all functions $f\colon \mathbb{Q}\to \mathbb{Q}$ such that, for all $x,y\in \mathbb{Q}$,
	\[f(x) f(y + 1) = f(x f(y)) + f(x)\]
\end{problem}

\begin{problem}	
	Decide whether there exist infinitely many triples $(a,b,c)$ of positive integers such that all prime factors of $a!+b!+c!$ are smaller than $2020$.
\end{problem}

\begin{problem}
	Each integer in $\{1, 2, 3, \ldots, 2020\}$ is coloured in such a way that, for all positive integers $a$ and $b$ such that $a+b \leq 2020$, the numbers $a$, $b$ and $a+b$ are not coloured with three different colours. Determine the maximum number of colours that can be used.
\end{problem}

\begin{problem}
Let $ABC$ be an acute scalene triangle, with the feet of $A, B, C$ onto $BC, CA, AB$ being $D, E, F$ respectively. Let $W$ be a point inside $ABC$ whose reflections over $BC, CA, AB$ are $W_a, W_b, W_c$ respectively. Finally, let $N$ and $I$ be the circumcentre and incentre of $W_aW_bW_c$ respectively. Prove that, if $N$ coincides with the nine-point centre of $DEF$, the line $WI$ is parallel to the Euler line of $ABC$.\nl
\emph{Note: If XYZ is a triangle with circumcentre O and orthocentre H, then the line OH is called the Euler line of XYZ and the midpoint of OH is called the nine-point centre of XYZ.}

\end{problem}

\end{document}
